CAT-DWAM, A Question Answering System

### 2011-05-07 paper/paper.tex
paper

For test answers, we searched the context of the answer for colocated units
matching what we found in the training corpus. We returned a score of 1 if there
was a unit and a score of 0 if there wasn't.
\subsubsection{Sequence Length}
% Mike

@@

We did pre-process some of the data by running the chunker (which creates
candidate phrases along with part of speech tags) and creating files in
groups of ten questions each with all of the candidates. Running the chunker
took about two minutes per question, so by doing this we were able to have
the whole set of potential candidates instantly ready to go.

>>>>

For test answers, we searched the context of the answer for colocated units
matching what we found in the training corpus. We returned a score of 1 if there
was a unit and a score of 0 if there wasn't.

\subsubsection{Sequence Length}
% Mike
This evaluation measures the difference between sequence length of the question
and the answer. It finds the length of the maximum sequence between the
question and answer and also finds the length of the maximum sequence between
the rewritten question and answer. A sequence is a list of (not necessarily 
consecutive) words that are shared by two sentences.

@@
